Export Markdown and latex using Emacs Org

### 2021-02-17 msteamc/index.tex
trivial update

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
\definecolor{mycolor}{RGB}{139,0,0}
\author{Eason}
\date{\today}
\title{Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)},
 pdfkeywords={},
 pdfsubject={This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.},
 pdfcreator={Emacs 26.3 (Org mode 9.3.7)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signal and System Chapter 1 Problems} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.

\section{Problem 1.1}
\label{sec:org3c85e3e}

\begin{prob}[]{prob:1.3}
Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
\begin{equation*}
\begin{array}{ccc}
 \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
 e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
 \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
\end{array}
\end{equation*}
\label{prob11}
\end{prob}

First, let's figure them out using the Euler's formula. For the nine complex
numbers in  \hyperref[prob11]{Problem 1.1}, we have:

\begin{eqnarray*}
\tfrac{1}{2} e^{i\pi } &=&  \tfrac{1}{2} (\cos(\pi) + i\sin(\pi) ) = \tfrac{1}{2} \cos(\pi) = -\tfrac{1}{2} \\
\tfrac{1}{2} e^{-i\pi} &=& \tfrac{1}{2}  (\cos(-\pi) + i\sin(-\pi) ) = \tfrac{1}{2} \cos(-\pi) = -\tfrac{1}{2} \\
e^{i\pi/2} &=& \cos(\pi/2) + i \sin(\pi/2) = i \\
e^{-i\pi/2} &=& \cos(-\pi/2) + i \sin(-\pi/2) = -i \\
e^{i5\pi/2} &=& \cos(5\pi/2) + i \sin(5\pi/2) = \cos(2\pi + \pi/2) + i \sin(2\pi + \pi/2) = i \sin(\pi/2) = i \\
\sqrt{2}e^{i\pi/4} &=& \sqrt{2} ( \cos(\pi/4) + i \sin(\pi/4) ) = \sqrt{2} ( \tfrac{\sqrt{2}}{2} + i\tfrac{\sqrt{2}}{2}  ) = 1 + i \\
 \sqrt{2} e^{i9 \pi/4} &=& \sqrt{2} ( \cos(9\pi/4) + i \sin(9\pi/4) ) = 1 + i \\
 \sqrt{2} e^{-i9 \pi/4} &=& \sqrt{2} ( \cos(-9\pi/4) + i \sin(-9\pi/4) ) = 1 - i \\
 \sqrt{2} e^{-i \pi/4} &=& \sqrt{2} ( \cos(-\pi/4) + i \sin(-\pi/4) ) = 1 - i
\end{eqnarray*}

\section{Problem 1.2}
\label{sec:orgbdb3cb8}

\begin{prob}[]{prob:1.3}
Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
 -\pi < \theta \leq \pi\)):
\begin{equation*}
\begin{array}{c{3cm}c{3cm}c{3cm}}
5 & -2 & -3i \\
\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
\end{array}
\end{equation*}
\label{prob12}
\end{prob}

For the nine complex numbers in  \hyperref[prob12]{Problem 1.2} , we have:

\begin{eqnarray*}
 5 &=& 5 e^{i0} = 5 e^{i(2\pi n)}, n\in \{\ldots, -2,-1,0,1,2,\ldots \} \\
 -2 &=& 2 e^{i\pi} = -2 e^{i0} \\
 -3i &=& 3 e^{-i\pi} \\
 \tfrac{1}{2} - i \tfrac{\sqrt{3}}{2}  &=& e^{-i\pi/3} \\
 1+i &=& \sqrt{2} e^{i\pi/4} \\
 (1-i)^{2} &=& ( \sqrt{2} e^{-i\pi/4} )^{2} = 2 e^{-i\pi/2} \\
 i(1-i) &=& 1 - i = \sqrt{2} e^{-i\pi/4} \\
 \tfrac{1+i}{1-i} &=& \tfrac{ \sqrt{2}e^{i\pi/4} } { \sqrt{2}e^{-i\pi/4} } = e^{i\pi/2} \\
 \tfrac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}} &=& \tfrac{ 2e^{i\pi/4} }{ 2 e^{i\pi/3} } = e^{-i\pi/12}
\end{eqnarray*}

Every complex number \(a+ib\) can be visualized in the complex plane
\(\mathbb{C}\). It can be viewed either as the point with the coordinate
\((a,b)\) or as a vector starting from \(( 0,0 )\) to the point \((a,b)\).

Also every complex number \(a+ib\) can be represented in the exponential form
conveniently by using the Euler's formula \(e^{i\alpha} = \cos\alpha +
 i\sin\alpha\). One complex number have unique Cartesian form but many
expoential forms. Taking \(1+i\) for example, its expoential form can be
\(\sqrt{2}e^{i(\pi/4 + 2n\pi)}, n\in \{ \ldots, -2,-1,0,1,2,\ldots \}\). When
we express a complex number in expoential form, it helps to keep a concept of
rotation in mind. In the complex plane \(\mathbb{C}\), a complex number will
return to itself if it rotates a multiple of \(2\pi\) around the origin point
with radius equal to its modulus. please keep the concept of roatation in mind
and it will become increasingly important during our later study.

In the development of complex analysis, \(a+ib\) has another form \(r\angle
 \theta\), where \(r\) is the modulus and \(\theta\) the argument (or the
angle). Obviously, this notation is not as good as the expoential form,
espacialy when we want to do complex analysis such as differentiation and
integration. We just mention it here for the sake of completion. The expoential
form will be deployed from now on.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
\end{center}

Now, let's go back to \hyperref[prob11]{Problem 1.1} and Problem \hyperref[prob12]{Problem
1.2}. It's easy to figure the answers out using the Euler's formula. Let's do
more to show them on the complex plane keeping the concept of rotation in mind.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/problem1_1.pdf}
\caption{\label{problem1-1}visualized the complex numbers from Problem \hyperref[prob11]{Problem 1.1} in the complex plan}
\end{figure}

From Figure \ref{problem1-1} , taking \(\color{green}{\tfrac{1}{2}e^{i\pi}}\) and
\(\color{red}{\tfrac{1}{2}e^{-i\pi}}\) for example, in the complex plane, they
are the same point \(-\tfrac{1}{2}\) which means \(-\tfrac{1}{2}\) can be
reached by rotating \(\tfrac{1}{2}\) with angle \(\pi\) anti-clockwise or with angle
\(-\pi\) clockwise. Essentially, this is because that \(e^{i\theta} =
 e^{i(\theta + 2n\pi)}, n\in \{\ldots,-2,-1,0,1,2,\ldots\}\). It's
straightforward that \(e^{i\pi} = e^{i(\pi + 2(-1)\pi)} = e^{-i\pi}\).

In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob12]{Problem 1.2}, I want to say
more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
methods to get the polar form:
\begin{enumerate}
\item multiply the fraction's numerator and denominator by \(( 1 + i )\)

So we have:
\begin{eqnarray*}
\frac{1+i}{1-i}& = & \frac{(1+i)(1+i)}{(1-i)(1+i)} \\
&=& \frac{2i}{2} = i
\end{eqnarray*}

\item express the numerator and denominator in expoential form first, then do the
following calculation.

\begin{eqnarray*}
\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
&=& e^{i2\pi/4} = e^{i\pi/2} = i
\end{eqnarray*}
\end{enumerate}
\section{Problem 1.3}
\label{sec:org975ac37}

\begin{prob}[]{prob:1.3}
Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
of the following signals:
\begin{equation*}
\begin{array}{ll}
\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} \\
 \mathrm{(c)} \quad x_{3}(t) = \cos(t) & \mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] \\
 \mathrm{( e )} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{(f)} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
\end{array}
\end{equation*}
\label{prob13}
\end{prob}

Before solving this problem, let's review the definition of \(P_{\infty}\) and
\(E_{\infty}\). For a continuous time signal \(x(t)\), we have
\begin{eqnarray}
\label{eq:2}
E_{\infty}&=& \lim_{T\to \infty} \int_{-T}^{T} |x(t)|^{2}\mathrm{d}t \\
P_{\infty}&=& \lim_{T\to \infty} \frac{1}{2T}\int_{-T}^{T} |x(t)|^{2}\mathrm{d}t = \lim_{T\to\infty} \frac{E_{\infty}}{2T}
\end{eqnarray}
For a discrete time signal \(x[n]\), we have:
\begin{eqnarray}
\label{eq:3}
E_{\infty}&=& \lim_{N\to \infty} \sum_{n=-N}^{+N} |x[n]|^{2} \\
P_{\infty}&=& \lim_{N\to \infty} \frac{1}{2N+1} \sum_{n=-N}^{+N} |x[n]|^{2} = \lim_{N\to\infty} \frac{E_{\infty}}{2N+1}
\end{eqnarray}

Equation (\ref{eq:2})(\ref{eq:3}) are not only mathmatical definitions but also
related to physical quantities such as power and energy in a physical system.
For an electric circuit, taking the voltage \(v(t)\) and current \(i(t)\) across
a resistor for example, the power at time \(t\) can be calculated by:
\begin{equation}
\label{eq:4}
p(t) = v(t)i(t) = \frac{v^{2}(t)}{R}
\end{equation}
Let's go back to equation (\ref{eq:2}) and equation(\ref{eq:3}), if
\(E_{\infty}< \infty\) we say that the signal has finite energy otherwise
infinite energy. If \(P_{\infty} <\infty\) we say that the signal has finite
power otherwise infinite power.

Next let's determine the values of \(P_{\infty}\) and \(E_{\infty}\) for the
given signals.
\subsection{Problem1.3a \(\mathbf{(a)}: x_{1}(t)= e^{-2t}u(t)\)}
\label{sec:orge15cb02}

\begin{eqnarray*}
E_{\infty}  & =  & \int_{\infty}^{\infty} |e^{-2t}u(t)|^{2} \mathrm{d}t \\
&=& \int_{0}^{\infty} e^{-4t} \mathrm{d}t \\
&=& \frac{1}{4}
\end{eqnarray*}
So, it's straightforward that:
\begin{equation}
\label{eq:5}
P_{\infty} = \lim_{T\to \infty} \frac{E_{\infty}}{2T}  = 0
\end{equation}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3.pdf}
\end{center}

\subsection{Problem1.3b \(\mathbf{(b)}: x_{2}(t)= e^{i(2t+\pi/4)}\)}
\label{sec:orgf93273c}

We have \(|e^{i(2t+\pi/4)}| = 1\) , therefore
\begin{eqnarray*}
E_{\infty}&=& \int_{\infty}^{\infty} |x_{2}(t)= e^{i(2t+\pi/4)}|^{2} \mathrm{d}t \\
&=& \infty
\end{eqnarray*}

For power \(P_{\infty}\), we have:
\begin{eqnarray*}
P_{\infty}&= &\lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{2}(t)|^{2} \mathrm{d}t  \\
&=& 1
\end{eqnarray*}

This signal has constant power. If you keep the concept of rotation mentioned in
Problem \ref{prob11}, you will notice immediately that all the points generated by
\(x_{2}(t)\) lies on the unit circle.

\subsection{Problem 1.3c \(\mathbf{(c)}:x_{3}(t)=\cos(t)\)}
\label{sec:org2d00fa8}

\begin{eqnarray*}
E_{\infty}&=& \lim_{T\to\infty} \int_{-\infty}^{\infty} |x_{3}(t)|^{2} \mathrm{d}t \\
&=& \int_{\infty}^{\infty} \cos(t)^{2} \mathrm{d}t = \infty
\end{eqnarray*}

\begin{eqnarray*}
P_{\infty}&=& \lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{3}(t)|^{2} \mathrm{d}t  \\
&=& \lim_{T\to\infty}\frac{1}{2T} \int_{-T}^{T} \cos(t)^{2} \mathrm{d}t \\
&=& \lim_{T\to\infty} \frac{1}{2T} \int_{-T}^{T} \frac{1+\cos(2t)}{2} \mathrm{d}t = \frac{1}{2}
\end{eqnarray*}

\(x_{3}(t)\)  can be visualized as follows:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3c.pdf}
\end{center}

\subsection{Problem 1.3d \(\mathbf{(d):} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n]\)}
\label{sec:org9332415}

By definition, we have:
\begin{eqnarray*}
E_{\infty}&=&\lim_{N\to\infty}\sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2} \\
&=&\lim_{N\to\infty}\sum_{n=0}^{N} (\tfrac{1}{4})^{n} \\
&=& \tfrac{4}{3}
\end{eqnarray*}

Then,
\begin{eqnarray*}
P_{\infty}&=& \lim_{N\to\infty} \frac{1}{2N+1} \sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2}   \\
&=& 0
\end{eqnarray*}

\(x_{1}[n]\) can visualized as:
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3d.pdf}
\end{center}

\section{Problem 1.4}
\label{sec:orgcfde750}

\begin{prob}[]{prob:1-4}
 Problem 1.4: Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
for each signal given below, determine the values of \(n\) for which it is
guaranteed to be zero.
\begin{eqnarray*}
\mathbf{ (a) } & & x[n-3] \\
\mathbf{ (b) } & & x[n+4] \\
\mathbf{ (c) } & & x[-n]  \\
\mathbf{ (d) } & & x[-n+2] \\
\mathbf{ (e) } & & x[-n-2]
\end{eqnarray*}
\label{prob:1-4}
\end{prob}

For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
of the variable \(n\) will change the interval in which the signals are zero.
For the convenience of calculation, we write the origin signal as:
\begin{equation*}
x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
\end{equation*}

We can visualize \(x(m)\) as below (I just give an example, you can name any
signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
\end{center}

\subsection{Problem 1.4a \(\mathbf{(a)}:x[n-3]\)}
\label{sec:org897c6ea}

For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
\begin{eqnarray*}
  m=n-3 &<& -2 \\
  m=n-3 &>& 4
\end{eqnarray*}
 Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can see that
the new signal is a right shift three relative to the origin signal, i.e. new
signal is delayed with three.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
\end{center}

\subsection{Problem 1.4b \(\mathbf{(b)}:x[n+4]\)}
\label{sec:org9176217}

For signal \(\mathbf{(b)}\), we have:
\begin{eqnarray*}
m=n+4&<&-2 \\
m=n+4&>&4
\end{eqnarray*}
Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
signal is a left shift four relative to the origin signal, i.e. new
signal is advanced with four.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
\end{center}

\subsection{Problem 1.4c \(\mathbf{(c)}: x[-n]\)}
\label{sec:org71c1184}

For signal \(\mathbf{( c )}\), we have:
\begin{eqnarray*}
m=-n&<&-2 \\
m=-n&>&4
\end{eqnarray*}

Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
signal is a reversal of the origin signal.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
\end{center}

\subsection{Problem 1.4d \(\mathbf{(d)}: x[-n+2]\)}
\label{sec:org0b89113}

for signal \(\mathbf{(d)}\), we have:
\begin{eqnarray*}
m=-n+2&<&-2 \\
m=-n+2&>&4
\end{eqnarray*}
Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
flip the original signal then right shift the flipped signal by 2. Notice the
contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
which I know that the minus symbol means reversal and \(-2\) means right
shift by 2.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
\end{center}

\subsection{Problem 1.4e \(\mathbf{(e)}: x[-n-2]\)}
\label{sec:org04ff18a}

For signal \(\mathbf{(e)}\), we have:

\begin{eqnarray*}
m=-n-2&<&-2 \\
m=-n-2&>&4
\end{eqnarray*}

Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
to filp the original signal first then left shift the flipped signal by two.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
\end{center}

\section{Problem 1.5}
\label{sec:org8c8f6ba}

\begin{prob}[]{prob:1-5}
Let \(x(t)\) be a signal with \(x(t)=0, \ x<3\). For each signal
given below, determine the values of \(t\) for which it is guaranteed to be
zero.

\begin{equation*}
\begin{array}{ll}
\mathbf{(a)}: x(1-t) \qquad  &   \mathbf{(b)}: x(1-t) + x(2-t)\qquad   \\
\mathbf{(c)}: x(1-t)x(2-t)\qquad &  \mathbf{(d)}: x(3t) \qquad  \\
  \mathbf{(e)}: x(t/3)\qquad & \\
\end{array}
\end{equation*}
\label{prob:1-5}
\end{prob}

For signal \(\mathbf{(a)}: x(1-t)\),  we have:
\begin{equation*}
1-t < 3
\end{equation*}

So, \(t>-2\). Signal \(\mathbf{(a)}: x(1-t)\) can be achieved by flipping the
origin signal first then right shifting one.

For signal \(\mathbf{(b)}: x(1-t) + x(2-t)\) , we have:
\begin{eqnarray*}
1-t&< &3 \\
2-t&<& 3
\end{eqnarray*}
Because it a "\(+\)" between \(x(1-t)\) and \(x(2-t)\) so only when both of the
two signals are zero, the result will be zero. For the first part we have the
value zero when \(t>-2\) the second \(t>-1\), so the result will be the
intersect of these two intervals, i.e. \(t>-1\) . we achieve signal
\(\mathbf{(b)}: x(1-t) + x(2-t)\) by adding signal \(\mathbf{(a)}: x(1-t)\)
with a second signal \(x(2-t)\) which can be achieved by flipping it first then
right shifting two.

For signal \(\mathbf{(c)}: x(1-t)x(2-t)\), \(x(1-t)\) is multiplied by
\(x(2-t)\), so if any one of these two signals is zero, the result is zero.
Based on the result of signal \(\mathbf{( b )}\), we have \(t>-2\).

For signal \(\mathbf{( d )}: x(3t)\), we have:
\begin{equation*}
3t < 3
\end{equation*}
Then, \(t<1\). The signal is compressed by \(3\).

For signal \(\mathbf{( e )}: x(t/3)\), we have:
\begin{equation*}
t/3 < 3
\end{equation*}
Then, \(t<9\). The signal is streched by \(3\).

\section{Problem 1.6}
\label{sec:orgb735a47}

\begin{prob}[]{prob:1-6}
Determine whether or not each of the following signals is periodic:

\begin{eqnarray*}
&&  \mathbf{(a)}: x_{1}(t) = 2e^{i(t+\pi/4)}u(t) \\
&&  \mathbf{( b )}: x_{2}[n] = u[n] + u[-n]  \\
&&  \mathbf{(c)}: x_{3}[n] = \sum_{k=-\infty}^{\infty} \{ \delta[n-4k] - \delta[n-1-4k] \}
\end{eqnarray*}
\label{prob:1-6}
\end{prob}

\begin{itemize}
\item \(x_{1}(t)\) is not periodic because \(u(t) = 0, t<0\)
\item \(x_{2}[n]\) is not periodic because
\begin{equation*}
x_{2}[n] =
\begin{cases}
2 & n=0 \\
1 & n\neq 0
\end{cases}
\end{equation*}
\item For signal \(x_{3}[n]\) we know that with a \(n\), \(\delta[n-4k]\) and
\(\delta[n-1-4k]\) can not be zero at the same time. Because \(k\) and
\(n-4k\) must be integers, \(\delta[n-4k]\) and \(\delta[n-1-4k]\) will repeat
themself every four steps. Furthermore, for every \(n\), the \(k\) runs from
\(-\infty\) to \(\infty\), and only one \(k\) will match the \(n\) to set
\(\delta[n-4k]\) or \(\delta[n-1-4k]\) as zero. We can test it by setting
\(n = 0,1,2,\ldots\)
\begin{eqnarray*}
&& x[0] = 1,\quad x[1] = -1, \quad x[2] = 0, \quad x[3] = 0 \\
&& x[4] = 1,\quad x[5] = -1, \quad x[6] = 0, \quad x[7] = 0 \\
&& x[8] = 1,\quad x[9] = -1, \quad x[10] = 0, \quad x[11] = 0
\end{eqnarray*}

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-6.pdf}
\end{center}
\end{itemize}

\section{Problem 1.7}
\label{sec:org292be4b}

\begin{prob}[]{prob:1-7}
For each signal given below, determine all the values of the independent
variable at which the even part of the signal is guaranteed to be zero.

\begin{equation*}
\small
\begin{array}{ll}
 \mathbf{(a)}: x_{1}[n] = u[n] - u[n-4] \qquad  &   \mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t) \qquad   \\
  \mathbf{(c)}: x_{3}[n] = (\frac{1}{2})^{n} u[n-3] \qquad &  \mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2) \\
\end{array}
\end{equation*}
\label{prob:1-7}
\end{prob}

\subsection{Problem 1.7a \(\mathbf{(a)}: x_{1}[n] = u[n] - u[n-4]\)}
\label{sec:orgcc2fcf2}

Any signal \(x_{1}(t)\) consists of two parts, even part \(\mathrm{Ev}
\{x_{1}(t)\}\) and odd part \(\mathrm{Od} \{ x_{1}(t)\}\). For signal \(\mathbf{(a)}\), when the signal is zero, we have the domain of the independent
value \(n< 0\) and \(n \geq 4\) , so the even part of the signal will be
zero when \(n\leq 4\) and \(n\geq 4\). \(x_{t}(t)\) and its even part and odd
part can be illustrated as:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ab.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ac.pdf}
\end{center}

\subsection{Problem 1.7b \(\mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t)\)}
\label{sec:orge473634}
For signal \(x_{2}(t) = \sin (\frac{1}{2} t)\), because it is an odd signal, so
for all \(t\), the even part of \(x_{2}(t)\) is zero.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-7b.pdf}
\end{center}

Notice that for \(\sin(\frac{1}{2}t)\), the signal can be obtained by streching
\(\sin(t)\) with a factor \(2\). In particular, the fundamental period is \(4\pi\).

\subsection{Problem 1.7c \(\mathbf{(c)}: x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\)}
\label{sec:orgbe754f7}

For signal \(x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\), which will be zeros for
\(n<3\). By definition, the even part of \(x_{3}[n]\) will be zeros for \(|n| <
3\). Actually, we do not visualize the signal to draw such a conclusion. For the
sake of visualization, I illustrate the signal as below:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7ca.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cb.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cc.pdf}
\end{center}

\subsection{Problem 1.7d \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\)}
\label{sec:orgca169be}

For signal \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\), we have \(x_{4}(t) = 0,\
t<-2\). Because the even and odd part is symmetrical with y-axis, there is no
\(t\) at which the even and odd part of will be zero.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7da.pdf}
\end{center}

\section{Problem 1.8}
\label{sec:org9d56250}

\begin{prob}[]{prob:1-8}
Express the real part of each of the following signals in the form
\(Ae^{-at}\cos(\omega t + \phi)\), where \(A,a,\omega, \phi\) are real numbers
with \(A>0\) and \(-\pi < \phi \leq \pi\):
\begin{equation*}
\small
\begin{array}{ll}
  \mathbf{( a )}: x_{1}(t) = -2 &  \mathbf{( b )}: x_{2}(t) = \sqrt{2}e^{i\pi/4}\cos(3t + 2\pi) \\
  \mathbf{( c )}: x_{3}(t) = e^{-t}\sin(3t + \pi) & \mathbf{( d )}: x_{4}(t) = i e^{(-2+i100)t}
\end{array}
\end{equation*}
\label{prob:1-8}
\end{prob}

>>>>

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
\definecolor{mycolor}{RGB}{139,0,0}
\author{Eason}
\date{\today}
\title{Export Markdown and latex using Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Export Markdown and latex using Emacs Org},
 pdfkeywords={},
 pdfsubject={set up the Emacs org and ox-hugo to export the org files in markdown and latex format.},
 pdfcreator={Emacs 26.3 (Org mode 9.3.7)},
 pdflang={English}}
\begin{document}

\hspace{0pt}\\

set up the Emacs org and ox-hugo to export the org files in markdown and latex format.

\section{Introduction}
\label{sec:orgc771d89}

I use hugo before it support Emacs org file. Then I use an Emacs extension
called \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} which is a carefully crafted Org exporter back-end for Hugo.
Ox-hugo meets all my requirement and definitely worth a try when you are an
advanced user of Emacs Org. By the way, if you are quite familiar with Emacs
Org, there is no need to take time to learn markdown. Emacs Org, I think, is
more elegant than markdown.

\section{set up ox-hugo}
\label{sec:orgd4e98d9}

I use Spacemacs and integrate ox-hugo into my config is easy. You can add it
into your private layer or just add it in your \texttt{user-config} . Please refer to
\href{https://github.com/kaushalmodi/ox-hugo}{the repo.} and read the document for more information.

The first time you want to export an Org file or a subtree of an Org file, use
\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
\section{use Org Macro replacement}
\label{sec:org3a92f3b}

Often, you want different actions when you export the Org file to
hugo-compatible markdown and latex file. For example, hugo or hugo theme supports
summary and shortcodes such as \texttt{alert note} and \texttt{alert warning} (see  \href{https://sourcethemes.com/academic/docs/writing-markdown-latex/}{Writing
content with Markdown, \LaTeX{}, and Shortcodes | Academic} )

When you export the snippet to markdown then hugo will display the content
according to the css. However, latex does not recognize the shortcodes. So latex
will display \texttt{\{ \{\% alert note \%\} \}} literally which is clutter. The Org Macro may
help. For more information please refer to \href{https://orgmode.org/manual/Macro-replacement.html}{The Org Manual: Macro replacement} and
\href{https://github.com/fniessen/org-macros}{fniessen/org-macros: Shared macros for Org mode} . I also define my own Org Macro
in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setup file for every .org file}. With Org Macro, I control some contents
and options exist only for certain backend.

Once you are familiar with Org Macro, It behaves beyond your imagination.
\section{use the setupfile for each Org file}
\label{sec:org956dd85}

Often, you options for a org file grows more and more. If you think it kind of
clutter at the top of your Org files, you can group them in a setupfile then
include it at the top of your Org file.

For my setupfiles, please refer to \href{https://github.com/msteamc/.spacemacs.d/tree/master/org-templates}{my org-templates}. As you can see, I have
several setupfiles for different aims. To include one of them in my Org file, I
use:

\texttt{\#+SETUPFILE: <path+name of the setup files>}

By using \texttt{\#+SETUPFILE} ,I only have to option lines at the top of my org file.
So it looks clean.

Also, you can notice that in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setupfile named enpost.org} exists options for
different export targets.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProbzzzzzzzz.pdf}
\end{center}
\end{document}
